---
title: "Firesummary"
author: "Derek Corcoran"
date: "August 25, 2016"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
```

#Abstract

This webpage will show the results of a bat survey study done in the Plumas National Forest in North California. The objective of this study is to determine the distribution of the different species of bats within the park. In order to do that we have performed occupancy models for the species present in the park. The results of this models will be shown as maps showing the probability of occurence of bats in each point, that is, if you see a value of 1, there is a 100% chance of finding a bat in that point, if there is a value of 0 there is 0% chance of finding that specie in that point, if there is a value of 0.5 there is a 50% chance of finding that specie in that point.

Another result

```{r, message=FALSE, warning=FALSE, echo=FALSE,results='hide'}
#first load libraries
library(raster)
library(rasterVis)
library(maps)
library(maptools)
library(rgdal)
library(latticeExtra)
library(dplyr)
library(knitr)
library(unmarked)
library(lubridate)
library(jpeg)
library(stargazer)
library(xtable)
library(MuMIn)
library(ggplot2)
library(RCurl)
library(foreign)
library(caret)
library(AICcmodavg)
library(viridis)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='hide', cache=TRUE}
Predictors<- readRDS("Predictors_Stack.rds")
PNF <- readRDS("PNF.rds")
```

```{r,echo=FALSE, warning=FALSE,message=FALSE}
Grandtotal <- read.csv("~/LastBat/Grandtotal.csv")
Grandtotal <- Grandtotal[,-1]

sampling.cov<- Grandtotal[,53:83]
sampling.cov <- sampling.cov[,-c(7,8,17:22)]
saveRDS(sampling.cov, "sampling.cov.rds")

#This next step changes according to the models
preprocov <-preProcess(sampling.cov[,15:23], method = c("center","scale"))
sampling.cov<-predict(preprocov, sampling.cov[,15:23])

Dailycov <- Grandtotal[,84:110]


preproDaily <-preProcess(Dailycov, method = c("center","scale"))
Dailycov<-predict(preproDaily, Dailycov)

Julian<-Dailycov[,1:3]
Max.hum<-Dailycov[,4:6]
Max.temp<-Dailycov[,7:9]
Mean.hum<-Dailycov[,10:12]
Mean.temp<-Dailycov[,13:15]
Min.hum<-Dailycov[,16:18]
Min.temp<-Dailycov[,19:21]
Sd.hum<-Dailycov[,22:24]
Sd.temp<-Dailycov[,25:27]

Dailycov<- list(Julian,Max.hum, Max.temp, Mean.hum,Mean.temp, Min.hum, Min.temp, Sd.hum, Sd.temp)
names(Dailycov) <- c("Julian", "Maxhum","Maxtemp","Meanhum", "Meantemp","Minhum","Mintemp","sdhum","sdtemp")

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

Pred.DF<-as.data.frame(Predictors)


Pred.DF<-predict(preprocov, new=Pred.DF)

Distance.to.water <- Predictors[[1]]  # this will be the template
Distance.to.water[] <- NA 
values(Distance.to.water)<-Pred.DF[,1]

Distance.to.road <- Predictors[[1]]  # this will be the template
Distance.to.road[] <- NA 
values(Distance.to.road)<-Pred.DF[,2]

Existing.vegetation <- Predictors[[1]]  # this will be the template
Existing.vegetation[] <- NA 
values(Existing.vegetation)<-Pred.DF[,3]

Altitude <- Predictors[[1]]  # this will be the template
Altitude[] <- NA 
values(Altitude)<-Pred.DF[,4]
     
Burn.intensity.soil <- Predictors[[1]]  # this will be the template
Burn.intensity.soil[] <- NA 
values(Burn.intensity.soil)<-Pred.DF[,5]

Burn.intensity.Canopy <- Predictors[[1]]  # this will be the template
Burn.intensity.Canopy[] <- NA 
values(Burn.intensity.Canopy)<-Pred.DF[,6]

Burn.intensity.basal <- Predictors[[1]]  # this will be the template
Burn.intensity.basal[] <- NA 
values(Burn.intensity.basal)<-Pred.DF[,7]

fire_dist <- Predictors[[1]]  # this will be the template
fire_dist[] <- NA 
values(fire_dist)<-Pred.DF[,8]

forest_dist <- Predictors[[1]]  # this will be the template
forest_dist[] <- NA 
values(forest_dist)<-Pred.DF[,9]

Predictors <-stack(Distance.to.water, Distance.to.road, Existing.vegetation, Altitude, Burn.intensity.soil,Burn.intensity.Canopy, Burn.intensity.basal, fire_dist, forest_dist)
names(Predictors)<-c("Distance to water", "Distance to road","Existing vegetation","Altitude", "Burn intensity soil","Burn intensity Canopy", "Burn intensity basal", "fire_dist", "forest_dist")


plot(Predictors)
```

#Results collected in the field 



#Maps showing the sampled Points


#Results of species prescence

In this area 0 means absence, and 1 means prescence. This table has for each site (ID), every specie and day, so for example if Mylu1=0, that means that for *Myotis lucifugus* (common name Little Brown bat, was detected on day one for that particular site).

##Here is a key for bat species

- *Myotis yumanensis* (Myyu)
- *Myotis californicus* (Myca)
- *Myotis ciliolabrum* (Myci)
- *Myotis volans* (Myvo)
- *Myotis lucifugus* (Mylu)
- *Parastrellus hesperus* (Pahe)
- *Lasiurus blossevillii* (Labo)
- *Myotis evotis* (Myev)
- *Antrozous pallidus*  **(Anpa)**
- *Eptesicus fuscus* (Epfu)
- *Lasionycteris noctivagans* (Lano)
- *Myotis thysanodes* **(Myth)**
- *Tadarida brasiliensis* (Tabr)
- *Lasiurus cinereus* (Laci)
- *Corynorhinus townsendii* **(Coto)**
- *Euderma maculatum* (Euma)
- *Eumops perotis* (Eupe)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccu <- Grandtotal[,2:52]
```

#Maps predicting the distribution of bats

##Yuma myotis (*Myotis yumanensis*)

```{r, echo=FALSE,message=FALSE}
library(unmarked)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}
#N=49a
BatOccuMyYu<-BatOccu[,1:3]

SimOccuMyYu2<-unmarkedFrameOccu(y = BatOccuMyYu, siteCovs =sampling.cov, obsCovs=Dailycov)

# Fit model with psi held constant
model.Occu1.My.Yu2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuMyYu2)

select.My.Yu2 <- dredge(model.Occu1.My.Yu2, rank = "AICc")
library(texreg)
htmlreg(extract(subset(select.My.Yu2, delta <= 1, recalc.weights = FALSE)))

model.Occu1.My.Yu2 <- occu(~ Meantemp + Minhum + Meanhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist,SimOccuMyYu2)

select.My.Yu2 <- dredge(model.Occu1.My.Yu2, rank = "AICc", subset= !(  
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`)& `p(Meantemp)`& `p(Meanhum)`& `p(Minhum)`)

best2.My.Yu2<-get.models(select.My.Yu2, 1)[[1]]
Occu1.layer.MyYu2 <- predict(best2.My.Yu2, type = "state", newdata=Predictors)

brks= c(0, 0.1, 0.2, 0.3, 0.4,0.5, 0.6,0.7, 0.8,0.9, 1)
cols <- magma(10)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

plot(Occu1.layer.MyYu2$Predicted, colNA="white", main="Occupancy estimation for Yuma Myotis",breaks=brks, lab.breaks=brks, col=cols, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.My.Yu2, delta <= 2, recalc.weights = TRUE)), file = "myyu.doc")

htmlreg(extract(subset(select.My.Yu2, delta <= 2, recalc.weights = TRUE)))
```

##California bat (*Myotis californicus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyCa<-BatOccu[,4:6]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}

SimOccuMyCa2<-unmarkedFrameOccu(y = BatOccuMyCa, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ca2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuMyCa2)

select.My.Ca2 <- dredge(model.Occu1.My.Ca2, rank = "AICc")
library(texreg)
htmlreg(extract(subset(select.My.Ca2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Ca2 <- occu(~ Maxhum + Meanhum + Meantemp + Mintemp ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyCa2)

select.My.Ca2 <- dredge(model.Occu1.My.Ca2, rank = "AICc", subset= !(
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Maxhum)` & `p(Meanhum)` & `p(Meantemp)` & `p(Mintemp)`)

best2.My.Ca2<-get.models(select.My.Ca2, 1)[[1]]
Occu1.layer.MyCa2 <- predict(best2.My.Ca2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
Occu1.layer.MyCa<-Occu1.layer.MyCa2
plot(Occu1.layer.MyCa$Predicted, colNA="white", main="Occupancy estimation for California Bat",breaks=brks, col=cols,lab.breaks=brks, zlim=c(0,1))
library(texreg)
htmlreg(extract(subset(select.My.Ca2, delta <= 2, recalc.weights = TRUE)))
```


##Western Small Footed Myotis (*Myotis ciliolabrum*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyCi<-BatOccu[,7:9]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuMyCi2<-unmarkedFrameOccu(y = BatOccuMyCi, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ci2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuMyCi2)

select.My.Ci2 <- dredge(model.Occu1.My.Ci2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.My.Ci2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Ci2 <- occu(~ Maxhum + Meanhum + sdhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyCi2)

select.My.Ci2 <- dredge(model.Occu1.My.Ci2, rank = "AICc", subset= !( 
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Maxhum)`  & `p(Meanhum)` & `p(sdhum)`)

best2.My.Ci2<-get.models(select.My.Ci2, 1)[[1]]
Occu1.layer.MyCi2 <- predict(best2.My.Ci2, type = "state", newdata=Predictors)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
PNF <- readRDS("PNF.rds")
Occu1.layer.MyCi<-Occu1.layer.MyCi2
plot(Occu1.layer.MyCi$Predicted*PNF, colNA="white", main="Occupancy estimation for Western Small Footed Myotis",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.My.Ci2, delta <= 2, recalc.weights = TRUE)))
```

##Hairy-winged bat (*Myotis volans*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuMyVo<-BatOccu[,10:12]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyVo2<-unmarkedFrameOccu(y = BatOccuMyVo, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Vo2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuMyVo2)

select.My.Vo2 <- dredge(model.Occu1.My.Vo2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.My.Vo2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Vo2 <- occu(~ Maxhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyVo2)

select.My.Vo2 <- dredge(model.Occu1.My.Vo2, rank = "AICc", subset= !( 
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`)& `p(Maxhum)`)

best2.My.Vo2<-get.models(select.My.Vo2, 1)[[1]]

Occu1.layer.MyVo2 <- predict(best2.My.Vo2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

Occu1.layer.MyVo<-Occu1.layer.MyVo2
plot(Occu1.layer.MyVo$Predicted*PNF, colNA="white", main="Occupancy estimation for Hairy-winged bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.My.Vo2, delta <= 2, recalc.weights = TRUE)))

```

##Little Brown bat (*Myotis lucifugus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyLu<-BatOccu[,13:15]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyLu2<-unmarkedFrameOccu(y = BatOccuMyLu, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Lu2 <-  occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuMyLu2)

select.My.Lu2 <- dredge(model.Occu1.My.Lu2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.My.Lu2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Lu2 <- occu(~ sdtemp ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyLu2)

select.My.Lu2 <- dredge(model.Occu1.My.Lu2, rank = "AICc", subset= !(  
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(sdtemp)`)

best2.My.Lu2<-get.models(select.My.Lu2, 1)[[1]]
Occu1.layer.MyLu2 <- predict(best2.My.Lu2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
library(texreg)

Occu1.layer.MyLu2<-Occu1.layer.MyLu2
plot(Occu1.layer.MyLu2$Predicted, colNA="white", main="Occupancy estimation for Little Brown Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

htmlreg(extract(subset(select.My.Lu2, delta <= 2, recalc.weights = TRUE)))
htmlreg(extract(subset(select.My.Lu2, delta <= 0.5, recalc.weights = TRUE)), file = "MYLU.doc")

```


##Western Red Bat (*Lasiurus blossevillii*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}

BatOccuLaBl<-BatOccu[,19:21]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}

SimOccuLaBl2<-unmarkedFrameOccu(y = BatOccuLaBl, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.La.Bl2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp~  1, SimOccuLaBl2)

select.La.Bl2 <- dredge(model.Occu1.La.Bl2, rank = "AICc")

htmlreg(extract(subset(select.La.Bl2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.La.Bl2 <- occu(~ sdtemp ~  Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuLaBl2)

select.La.Bl2 <- dredge(model.Occu1.La.Bl2, rank = "AICc", subset= !(  
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(sdtemp)`)

best2.La.Bl2<-get.models(select.La.Bl2, 1)[[1]]
Occu1.layer.LaBl2 <- predict(best2.La.Bl2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

Occu1.layer.LaBl2<-Occu1.layer.LaBl2
plot(Occu1.layer.LaBl2$Predicted*PNF, colNA="white", main="Occupancy estimation for Western Red Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.La.Bl2, delta <= 2, recalc.weights = TRUE)))
```

##Long-eared Bat (*Myotis evotis*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuMyEv<-BatOccu[,22:24]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyEv2<-unmarkedFrameOccu(y = BatOccuMyEv, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ev2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuMyEv2)

select.My.Ev2 <- dredge(model.Occu1.My.Ev2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.My.Ev2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Ev2 <- occu(~ Maxhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyEv2)

select.My.Ev2 <- dredge(model.Occu1.My.Ev2, rank = "AICc", subset= !(  
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`)  & `p(Maxhum)`)

best2.My.Ev2<-get.models(select.My.Ev2, 1)[[1]]
Occu1.layer.MyEv2 <- predict(best2.My.Ev2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}
Occu1.layer.MyEv2<-Occu1.layer.MyEv2
plot(Occu1.layer.MyEv2$Predicted, colNA="white", main="Occupancy estimation for Long Eared Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.My.Ev2, delta <= 2, recalc.weights = TRUE)))
```

## Pallid Bat (*Antrozous pallidus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuAnPa<-BatOccu[,25:27]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49

SimOccuAnPa2<-unmarkedFrameOccu(y = BatOccuAnPa, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.An.Pa2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuAnPa2)

select.An.Pa2 <- dredge(model.Occu1.An.Pa2, rank = "AICc")
library(texreg)
htmlreg(extract(subset(select.An.Pa2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.An.Pa2 <- occu(~ Julian ~Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuAnPa2)

select.An.Pa2 <- dredge(model.Occu1.An.Pa2, rank = "AICc", subset= !( 
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) &`p(Julian)`)



best2.An.Pa2<-get.models(select.An.Pa2, 1)[[1]]
Occu1.layer.AnPa2 <- predict(best2.An.Pa2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

Occu1.layer.AnPa2<-Occu1.layer.AnPa2
plot(Occu1.layer.AnPa2$Predicted*PNF, colNA="white", main="Occupancy estimation for Pallid Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.An.Pa2, delta <= 2, recalc.weights = TRUE)))
```


###Fringed Bat (*Myotis thysanoides*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyTh<-BatOccu[,34:36]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyTh2<-unmarkedFrameOccu(y = BatOccuMyTh, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Th2 <-occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuMyTh2)


select.My.Th2 <- dredge(model.Occu1.My.Th2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.My.Th2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.My.Th2 <- occu(~ Meanhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuMyTh2)


select.My.Th2 <- dredge(model.Occu1.My.Th2, rank = "AICc", subset= !(   
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) &`p(Meanhum)`)

best2.My.Th2<-get.models(select.My.Th2, 1)[[1]]
Occu1.layer.MyTh2 <- predict(best2.My.Th2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}
Occu1.layer.MyTh2<-Occu1.layer.MyTh2
plot(Occu1.layer.MyTh2$Predicted*PNF, colNA="white", main="Occupancy estimation for Fringed Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.My.Th2, delta <= 2, recalc.weights = TRUE)))
```

##Townsend’s Long-eared Bat (*Corynorhinus townsendii*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuCoTo<-BatOccu[,43:45]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuCoTo2<-unmarkedFrameOccu(y = BatOccuCoTo, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Co.To2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuCoTo2)


select.Co.To2 <- dredge(model.Occu1.Co.To2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.Co.To2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.Co.To2 <- occu(~ Meanhum + Mintemp + sdhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuCoTo2)


select.Co.To2 <- dredge(model.Occu1.Co.To2, rank = "AICc", subset= !( 
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`)& `p(Meanhum)`&`p(Mintemp)` &`p(sdhum)`)


best2.Co.To2<-get.models(select.Co.To2, 1)[[1]]
Occu1.layer.CoTo2 <- predict(best2.Co.To2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

Occu1.layer.CoTo2<-Occu1.layer.CoTo2
plot(Occu1.layer.CoTo2$Predicted*PNF, colNA="white", main="Occupancy estimation for Townsend big eared bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))


htmlreg(extract(subset(select.Co.To2, delta <= 2, recalc.weights = TRUE)))
```

##The western pipistrelle (*Parastrellus hesperus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuPaHe<-BatOccu[,16:18]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuPaHe2<-unmarkedFrameOccu(y = BatOccuPaHe, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Pa.He2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuPaHe2)

select.Pa.He2 <- dredge(model.Occu1.Pa.He2, rank = "AICc")

library(texreg)
htmlreg(extract(subset(select.Pa.He2, delta <= 2, recalc.weights = TRUE)))

model.Occu1.Pa.He2 <- occu(~ Julian + Maxhum + Mintemp ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuPaHe2)

select.Pa.He2 <- dredge(model.Occu1.Pa.He2,rank = "AICc", subset= !(
`psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
`psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
`psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Julian)` & `p(Maxhum)` & `p(Mintemp)`)


best2.Pa.He2<-get.models(select.Pa.He2, 1)[[1]]
Occu1.layer.PaHe2 <- predict(best2.Pa.He2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}
Occu1.layer.PaHe2<-Occu1.layer.PaHe2
plot(Occu1.layer.PaHe2$Predicted, colNA="white", main="Occupancy estimation for Pipistrel",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))

library(texreg)
htmlreg(extract(subset(select.Pa.He2, delta <= 2, recalc.weights = TRUE)))
```

##big brown bat (*Eptesicus fuscus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuEpFu<-BatOccu[,28:30]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
# SimOccuEpFu2<-unmarkedFrameOccu(y = BatOccuEpFu, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# model.Occu1.Ep.Fu2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuEpFu2)
# 
# select.Ep.Fu2 <- dredge(model.Occu1.Ep.Fu2, rank = "AICc")
# 
# library(texreg)
# htmlreg(extract(subset(select.Ep.Fu2, delta <= 2, recalc.weights = TRUE)))
# 
# model.Occu1.Ep.Fu2 <- occu(~ Julian + Meantemp + Meanhum ~  Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuEpFu2)
# 
# 
# select.Ep.Fu2 <- dredge(model.Occu1.Ep.Fu2, rank = "AICc", subset= !(  
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Julian)` & `p(Meantemp)` & `p(Meanhum)`)
# 
# best2.Ep.Fu2<-get.models(select.Ep.Fu2, 1)[[1]]
# Occu1.layer.EpFu2 <- predict(best2.Ep.Fu2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

# 
# Occu1.layer.EpFu2<-Occu1.layer.EpFu2
# plot(Occu1.layer.EpFu2$Predicted, colNA="white", main="Occupancy estimation for Big Brown Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# library(texreg)
# htmlreg(extract(subset(select.Ep.Fu2, delta <= 2, recalc.weights = TRUE)))
```

##silver-haired bat (*Lasionycteris noctivagans*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
#BatOccuLaNo<-BatOccu[,31:33]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
# SimOccuLaNo2<-unmarkedFrameOccu(y = BatOccuLaNo, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# model.Occu1.La.No2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuLaNo2)
# 
# 
# select.La.No2 <- dredge(model.Occu1.La.No2, rank = "AICc")
# 
# library(texreg)
# htmlreg(extract(subset(select.La.No2, delta <= 2, recalc.weights = TRUE)))
# 
# model.Occu1.La.No2 <- occu(~ Meantemp + Maxhum ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuLaNo2)
# 
# select.La.No2 <- dredge(model.Occu1.La.No2, rank = "AICc", subset= !( 
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`)& `p(Meantemp)` & `p(Maxhum)`)
# 
# 
# htmlreg(extract(subset(select.La.No2, delta <= 2, recalc.weights = TRUE)))
# 
# best2.La.No2<-get.models(select.La.No2, 1)[[1]]
# 
# Occu1.layer.LaNo2 <- predict(best2.La.No2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

# Occu1.layer.LaNo2<-Occu1.layer.LaNo2
# plot(Occu1.layer.LaNo2$Predicted, colNA="white", main="Occupancy estimation for Silver Haired Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# 
# library(texreg)
# htmlreg(extract(subset(select.La.No2, delta <= 2, recalc.weights = TRUE)))
```


##Brazilian free-tailed bat (*Tadarida brasiliensis*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
#BatOccuTaBr<-BatOccu[,37:39]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
# SimOccuTaBr2<-unmarkedFrameOccu(y = BatOccuTaBr, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# 
# model.Occu1.Ta.Br2 <-occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1,  SimOccuTaBr2)
# 
# select.Ta.Br2 <- dredge(model.Occu1.Ta.Br2, rank = "AICc")
# 
# htmlreg(extract(subset(select.Ta.Br2, delta <= 2, recalc.weights = TRUE)))
# 
# 
# model.Occu1.Ta.Br2 <-occu(~ Meanhum + sdhum + Minhum ~  Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist,  SimOccuTaBr2)
# 
# select.Ta.Br2 <- dredge(model.Occu1.Ta.Br2,rank = "AICc", subset= !(   
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(sdhum)` & `p(Meanhum)`& `p(Minhum)`)
# 
# 
# best2.Ta.Br2<-get.models(select.Ta.Br2, 1)[[1]]
# Occu1.layer.TaBr2 <- predict(best2.Ta.Br2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

# Occu1.layer.TaBr2<-Occu1.layer.TaBr2
# plot(Occu1.layer.TaBr2$Predicted, colNA="white", main="Occupancy estimation for Brazilian free-tailed bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# 
# library(texreg)
# htmlreg(extract(subset(select.Ta.Br2, delta <= 2, recalc.weights = TRUE)))
```


##hoary bat (*Lasiurus cinereus*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
#BatOccuLaCi<-BatOccu[,40:42]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
# SimOccuLaCi2<-unmarkedFrameOccu(y = BatOccuLaCi, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# model.Occu1.La.Ci2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuLaCi2)
# 
# 
# select.La.Ci2 <- dredge(model.Occu1.La.Ci2, rank = "AICc")
# 
# library(texreg)
# htmlreg(extract(subset(select.La.Ci2, delta <= 2, recalc.weights = TRUE)))
# 
# 
# model.Occu1.La.Ci2 <- occu(~  Julian + Meantemp + sdtemp + Minhum ~  Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuLaCi2)
# 
# 
# select.La.Ci2 <- dredge(model.Occu1.La.Ci2, rank = "AICc", subset= !( 
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Julian)` & `p(Meantemp)`& `p(sdtemp)`& `p(Minhum)`)
# 
# 
# best2.La.Ci2<-get.models(select.La.Ci2, 1)[[1]]
# Occu1.layer.LaCi2 <- predict(best2.La.Ci2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

# Occu1.layer.LaCi2<-Occu1.layer.LaCi2
# plot(Occu1.layer.LaCi2$Predicted, colNA="white", main="Occupancy estimation for Hoary Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# 
# library(texreg)
# htmlreg(extract(subset(select.La.Ci2, delta <= 2, recalc.weights = TRUE)))
```

##Spotted bat (*Euderma maculatum*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
#BatOccuEuMa<-BatOccu[,46:48]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
# SimOccuEuMa2<-unmarkedFrameOccu(y = BatOccuEuMa, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# model.Occu1.Eu.Ma2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuEuMa2)
# 
# select.Eu.Ma2 <- dredge(model.Occu1.Eu.Ma2, rank = "AICc")
# 
# library(texreg)
# htmlreg(extract(subset(select.Eu.Ma2, delta <= 2, recalc.weights = TRUE)))
# 
# model.Occu1.Eu.Ma2 <- occu(~ Meantemp + Maxtemp + Maxhum ~Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuEuMa2)
# 
# select.Eu.Ma2 <- dredge(model.Occu1.Eu.Ma2, rank = "AICc", subset= !( 
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Meantemp)`& `p(Maxtemp)` & `p(Maxhum)`)
# 
# best2.Eu.Ma2<-get.models(select.Eu.Ma2, 1)[[1]]
# Occu1.layer.EuMa2 <- predict(best2.Eu.Ma2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}
# 
# Occu1.layer.EuMa2<-Occu1.layer.EuMa2
# plot(Occu1.layer.EuMa2$Predicted, colNA="white", main="Occupancy estimation for Spotted Bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# 
# library(texreg)
# htmlreg(extract(subset(select.Eu.Ma2, delta <= 2, recalc.weights = TRUE)))
```


## western mastiff bat (*Eumops perotis*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
#BatOccuEuPe<-BatOccu[,49:51]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}
# #N=49
# 
# SimOccuEuPe2<-unmarkedFrameOccu(y = BatOccuEuPe, siteCovs =sampling.cov, obsCovs=Dailycov)
# 
# model.Occu1.Eu.Pe2 <- occu(~ Julian + Meanhum + Meantemp + sdhum + sdtemp + Maxhum + Maxtemp + Minhum + Mintemp ~  1, SimOccuEuPe2)
# 
# 
# select.Eu.Pe2 <- dredge(model.Occu1.Eu.Pe2, rank = "AICc")
# 
# #library(texreg)
# #htmlreg(extract(subset(select.Eu.Pe2, delta <= 2, recalc.weights = TRUE)))
# 
# model.Occu1.Eu.Pe2 <- occu(~ Maxhum + Meanhum + Minhum + sdhum  ~ Burn.intensity.Canopy + I(Burn.intensity.Canopy^2) + Burn.intensity.basal + I(Burn.intensity.basal^2) + fire_dist + forest_dist, SimOccuEuPe2)
# 
# 
# select.Eu.Pe2 <- dredge(model.Occu1.Eu.Pe2, rank = "AICc", subset= !(  
# `psi(Burn.intensity.Canopy)` && `psi(Burn.intensity.basal)` ||
# `psi(Burn.intensity.Canopy)` && `psi(I(Burn.intensity.basal^2))` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(Burn.intensity.basal)` ||
# `psi(I(Burn.intensity.Canopy^2))` && `psi(I(Burn.intensity.basal^2))`) & `p(Minhum)`& `p(sdhum)` & `p(Meanhum)`& `p(Maxhum)`)
# 
# best2.Eu.Pe2<-get.models(select.Eu.Pe2, 1)[[1]]
# Occu1.layer.EuPe2 <- predict(best2.Eu.Pe2, type = "state", newdata=Predictors)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
# 
# Occu1.layer.EuPe2<-Occu1.layer.EuPe2
# plot(Occu1.layer.EuPe2$Predicted*PNF, colNA="white", main="Occupancy estimation for western mastiff bat",breaks=brks, col=cols, lab.breaks=brks, zlim=c(0,1))
# 
# library(texreg)
# htmlreg(extract(subset(select.Eu.Pe2, delta <= 2, recalc.weights = TRUE)))
```

#Relationships between different species of Bats


#Fire bats


```{r,echo=FALSE, cache=TRUE, fig.width=6, fig.height=6}
#N=49a
# FireBats<-stack(Occu1.layer.MyYu2$Predicted, Occu1.layer.MyCa2$Predicted*PNF, Occu1.layer.MyCi2$Predicted*PNF,Occu1.layer.MyVo2$Predicted*PNF,Occu1.layer.MyLu2$Predicted*PNF, Occu1.layer.LaBl2$Predicted*PNF, Occu1.layer.MyEv2$Predicted*PNF,Occu1.layer.AnPa2$Predicted*PNF, Occu1.layer.MyTh2$Predicted*PNF, Occu1.layer.CoTo2$Predicted*PNF, Occu1.layer.PaHe2$Predicted*PNF, Occu1.layer.EpFu2$Predicted*PNF, Occu1.layer.LaNo2$Predicted*PNF, Occu1.layer.TaBr2$Predicted*PNF, Occu1.layer.LaCi2$Predicted*PNF, Occu1.layer.EuMa2$Predicted*PNF,Occu1.layer.EuPe2$Predicted*PNF)
# names(FireBats)<-c("MYYU", "MYCA","MYCI", "MYVO" ,"MYLU", "LABL","MYEV" ,"ANPA", "MYTH", "COTO", "PAHE", "EPFU","LANO", "TABR", "LACI", "EUMA", "EUPE")
# 
# library(viridis)
# levelplot(FireBats, col.regions = magma(99), colorkey = list(space = "bottom"))
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

# raster.values <- raster::extract(FireBats, cbind(Grandtotal$LONG, Grandtotal$LAT))
# summary(raster.values)
# Predictors<- readRDS("Predictors_Stack.rds")
# 
# fire.values <- raster::extract(Predictors, cbind(Grandtotal$LONG, Grandtotal$LAT))
# 
# fire.values <- data.frame(fire.values)
# 
# fire.values <- (fire.values$Burn.intensity.Canopy + fire.values$Burn.intensity.basal)/2
# 
# hist(fire.values)
# 
# raster.values <- cbind(raster.values, fire.values)
# raster.values <- data.frame(raster.values)
# raster.values = within(raster.values, {
#     FIRE = as.factor(ifelse(fire.values == 0, "No Fire", "Fire"))
#  })
# 
# summary(raster.values)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

# library(reshape)
# mdata <- melt(raster.values, id="FIRE")
# 
# mdata
# 
# 
# 	
# 
# library(ggplot2)
# library(plotrix) # for std error function
# library(dplyr) # for group_by and summarise_each function
# library(ggplot2)
# 
# ggplot(aes(y = value, x = FIRE), data = mdata[1:2091,]) + geom_boxplot()
# 
# ggplot(aes(y = value, x = variable, fill = FIRE), data = mdata[1:2091,]) + geom_boxplot()
# 
# # Group data by when and site
# grouped_df1<-group_by(mdata[1:2091,], variable , FIRE)
# 
# #summarise grouped data and calculate mean and standard error using function mean and std.error(from plotrix)
# summarised_df1<-summarise_each(grouped_df1,funs(mean=mean(., na.rm = TRUE),std_error=std.error))
# 
# summarised_df2<-summarise_each(grouped_df1,funs(mean=mean(., na.rm = TRUE),std_error=std.error, n = sum(!is.na(.))))
# 
# kable(summarised_df2)
# 
# # Define the top and bottom of the errorbars
# limits <- aes(ymax = mean + std_error, ymin=mean-std_error)
# 
# #Begin your ggplot
# #Here we are plotting site vs mean and filling by another factor variable when
# g<-ggplot(summarised_df1,aes(y = mean, x = reorder(variable, -mean), fill = FIRE))
# 
# #Creating bar to show the factor variable position_dodge 
# #ensures side by side creation of factor bars
# g<-g+geom_bar(stat = "identity",position = position_dodge())
# 
# #creation of error bar
# g<-g+geom_errorbar(limits,width=0.25,position = position_dodge(width = 0.9))
# #print graph
# 
# 
# g + theme(axis.text.x=element_text(angle = 90))+ 
#   xlab("Species") + ylab("Mean Occupancy")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
# names(Predictors)<-c("Distance to water", "Distance to road","Existing vegetation","Altitude", "Burn intensity soil","Burn intensity Canopy", "Burn intensity basal", "Distance to fire", "Distance to forest")
#  Fire_Predictors <- Predictors[[c(6,7,8,9)]]*PNF
#  
# names(Fire_Predictors) <- c("Burn intensity Canopy", "Burn intensity basal", "Distance to fire", "Distance to forest")
# 
# plot(Fire_Predictors)
# 
# just.fire <- Fire_Predictors[[1]]
# plot(just.fire, main = "Fire Intensity")
```


```{r, echo=FALSE}
# library(broom)
# species <- unique(mdata$variable)
# species
# DATA <- list()
# TEST <- list()
# TIDY <- list
# 
# for (i in 1:17)
# {
#   DATA [[i]] <- filter(mdata, variable == species [i])
#   TEST [[i]] <- try(t.test(filter(DATA[[i]], FIRE == "Fire")$value, filter(DATA[[i]], FIRE == "No Fire")$value))
#   if(inherits(res, "try-error"))
#   {
#     #error handling code, maybe just skip this iteration using
#     continue
#   }
# }
# 
# TIDY <- tidy(TEST[[1]])
# TIDY2 <- tidy(TEST[[2]])
# TIDY3 <- tidy(TEST[[3]])
# TIDY5 <- tidy(TEST[[5]])
# TIDY6 <- tidy(TEST[[6]])
# TIDY7 <- tidy(TEST[[7]])
# TIDY8 <- tidy(TEST[[8]])
# TIDY9 <- tidy(TEST[[9]])
# TIDY11 <- tidy(TEST[[11]])
# TIDY12 <- tidy(TEST[[12]])
# TIDY13 <- tidy(TEST[[13]])
# TIDY14 <- tidy(TEST[[14]])
# TIDY15 <- tidy(TEST[[15]])
# TIDY16 <- tidy(TEST[[16]])
# TIDY17 <- tidy(TEST[[17]])
# 
# SUPER <- list(TIDY, TIDY2, TIDY3, TIDY5, TIDY6, TIDY7, TIDY8, TIDY9, TIDY11, TIDY12, TIDY13, TIDY14, TIDY15, TIDY16, TIDY17)
# 
# 
# SUPER <- do.call("rbind", SUPER)
# 
# 
# SUPER <- cbind(species[-c(4,10,18)], SUPER)
# 
# SUPER <- SUPER[,c(1,3,4,6)]
# colnames(SUPER) <- c("Species", "Occupancy Fire", "Occupancy No Fire", "P-value")
# 
# kable(SUPER)
# 
# write.csv(SUPER, "super.csv")
# Models <- list(filter(select.My.Yu2, AICc == min(AICc)), filter(select.My.Ca2, AICc == min(AICc)), filter(select.My.Ci2, AICc == min(AICc)), filter(select.My.Vo2, AICc == min(AICc)), filter(select.My.Lu2, AICc == min(AICc)), filter(select.La.Bl2, AICc == min(AICc)), filter(select.My.Ev2, AICc == min(AICc)), filter(select.An.Pa2, AICc == min(AICc)), filter(select.My.Th2, AICc == min(AICc)), filter(select.Co.To2, AICc == min(AICc)),filter(select.Pa.He2 , AICc == min(AICc)), filter(select.Ep.Fu2, AICc == min(AICc)), filter(select.La.No2, AICc == min(AICc)), filter(select.Ta.Br2, AICc == min(AICc)), filter(select.La.Ci2, AICc == min(AICc)), filter(select.Eu.Ma2, AICc == min(AICc)), filter(select.Eu.Pe2, AICc == min(AICc)))
# Species<- c("MYYU", "MYCA", "MYCI", "MYVO","MYLU","LABL", "MYEV", "ANPA","MYTH", "COTO","PAHE", "EPFU","LANO","TABR","LACI","EUMA", "EUPE")
# 
# for (i in 1:length(Species)){
#   Models[[i]]$Species <- Species[i]
# }
# 
# models <- full_join(Models[[1]], Models[[2]])
# models <- full_join(models, Models[[3]])
# models <- full_join(models, Models[[4]])
# models <- full_join(models, Models[[5]])
# models <- full_join(models, Models[[6]])
# models <- full_join(models, Models[[7]])
# models <- full_join(models, Models[[8]])
# models <- full_join(models, Models[[9]])
# models <- full_join(models, Models[[10]])
# models <- full_join(models, Models[[11]])
# models <- full_join(models, Models[[12]])
# models <- full_join(models, Models[[13]])
# models <- full_join(models, Models[[14]])
# models <- full_join(models, Models[[15]])
# models <- full_join(models, Models[[16]])
# models <- full_join(models, Models[[17]])
# 
# colnames(models) <- gsub("\\)","",gsub("p\\(", "",gsub("I\\(", "",gsub("psi\\(", "",colnames(models)))))
# colnames(models)
# MODELS <- models[,c(17,3:8)] 
# MODELS2 <- models[,c(17,9:11,18:23)] 
# 
# models[,-17] <- ifelse(is.na(models[,-17]), 0 , 1)
# 
# 
# Occupancy.table <- models[,c(17,3:8)]
# 
# Total.occupancy <- c("Total", colSums(Occupancy.table[,-1]))
# Total <- c(rowSums(Occupancy.table[,-1]), "")
# 
# Occupancy.table <- rbind(MODELS,Total.occupancy)
# 
# Total
# length(Total)
# kable(cbind(Occupancy.table, Total))
# Occupancy.table <- cbind(Occupancy.table, Total)
# write.csv(Occupancy.table, "occupancytable2.csv")
# 
# #####################Detection#################################
# 
# Detection.table <- models[,c(17,9:11,18:23)]
# 
# Total.detection <- c("Total", colSums(Detection.table[,-1]))
# Total <- c(rowSums(Detection.table[,-1]), "")
# 
# Detection.table <- rbind(MODELS2,Total.detection)
# 
# Total
# length(Total)
# kable(cbind(Detection.table, Total))
# Detection.table <- cbind(Detection.table, Total)
# write.csv(Detection.table, "Detectiontable2.csv")
```
#Goodnes of fit
##MYYU

```{r, cache=TRUE, echo=FALSE}
# best2.My.Yu2@data@siteCovs[is.na(best2.My.Yu2@data@siteCovs)] <- 0
# best2.My.Yu2@data@obsCovs[is.na(best2.My.Yu2@data@obsCovs)] <- 0
# best2.My.Yu2@data@y[is.na(best2.My.Yu2@data@y)] <- 0
# obs.boot <- mb.gof.test(best2.My.Yu2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)
```

##MYCA

```{r, cache=TRUE, echo=FALSE}
# best2.My.Ca2@data@siteCovs[is.na(best2.My.Ca2@data@siteCovs)] <- 0
# best2.My.Ca2@data@obsCovs[is.na(best2.My.Ca2@data@obsCovs)] <- 0
# best2.My.Ca2@data@y[is.na(best2.My.Ca2@data@y)] <- 0
# obs.boot <- mb.gof.test(best2.My.Ca2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##MYCI

```{r, cache=TRUE, echo=FALSE}

# best2.My.Ci2@data@siteCovs[is.na(best2.My.Ci2@data@siteCovs)] <- 0
# best2.My.Ci2@data@obsCovs[is.na(best2.My.Ci2@data@obsCovs)] <- 0
# best2.My.Ci2@data@y[is.na(best2.My.Ci2@data@y)] <- 0
# obs.boot <- mb.gof.test(best2.My.Ci2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)
```

##MYVO

```{r, cache=TRUE, echo=FALSE}
# best2.My.Vo2@data@siteCovs[is.na(best2.My.Vo2@data@siteCovs)] <- 0
# best2.My.Vo2@data@obsCovs[is.na(best2.My.Vo2@data@obsCovs)] <- 0
# best2.My.Vo2@data@y[is.na(best2.My.Vo2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.My.Vo2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##MYLU

```{r, cache=TRUE, echo=FALSE}
# best2.My.Lu2@data@siteCovs[is.na(best2.My.Lu2@data@siteCovs)] <- 0
# best2.My.Lu2@data@obsCovs[is.na(best2.My.Lu2@data@obsCovs)] <- 0
# best2.My.Lu2@data@y[is.na(best2.My.Lu2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.My.Lu2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##LABL

```{r, cache=TRUE, echo=FALSE}
# best2.La.Bl2@data@siteCovs[is.na(best2.La.Bl2@data@siteCovs)] <- 0
# best2.La.Bl2@data@obsCovs[is.na(best2.La.Bl2@data@obsCovs)] <- 0
# best2.La.Bl2@data@y[is.na(best2.La.Bl2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.La.Bl2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##MYEV

```{r, cache=TRUE, echo=FALSE}

# best2.My.Ev2@data@siteCovs[is.na(best2.My.Ev2@data@siteCovs)] <- 0
# best2.My.Ev2@data@obsCovs[is.na(best2.My.Ev2@data@obsCovs)] <- 0
# best2.My.Ev2@data@y[is.na(best2.My.Ev2@data@y)] <- 0
# obs.boot <- mb.gof.test(best2.My.Ev2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##ANPA

```{r, cache=TRUE, echo=FALSE}
# best2.An.Pa2@data@siteCovs[is.na(best2.An.Pa2@data@siteCovs)] <- 0
# best2.An.Pa2@data@obsCovs[is.na(best2.An.Pa2@data@obsCovs)] <- 0
# best2.An.Pa2@data@y[is.na(best2.An.Pa2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.An.Pa2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##MYTH

```{r, cache=TRUE, echo=FALSE}
# best2.My.Th2@data@siteCovs[is.na(best2.My.Th2@data@siteCovs)] <- 0
# best2.My.Th2@data@obsCovs[is.na(best2.My.Th2@data@obsCovs)] <- 0
# best2.My.Th2@data@y[is.na(best2.My.Th2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.My.Th2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##COTO

```{r, cache=TRUE, echo=FALSE}
# best2.Co.To2@data@siteCovs[is.na(best2.Co.To2@data@siteCovs)] <- 0
# best2.Co.To2@data@obsCovs[is.na(best2.Co.To2@data@obsCovs)] <- 0
# best2.Co.To2@data@y[is.na(best2.Co.To2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Co.To2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##PAHE

```{r, cache=TRUE, echo=FALSE}
# best2.Pa.He2@data@siteCovs[is.na(best2.Pa.He2@data@siteCovs)] <- 0
# best2.Pa.He2@data@obsCovs[is.na(best2.Pa.He2@data@obsCovs)] <- 0
# best2.Pa.He2@data@y[is.na(best2.Pa.He2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Pa.He2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##EPFU

```{r, cache=TRUE, echo=FALSE}
# best2.Ep.Fu2@data@siteCovs[is.na(best2.Ep.Fu2@data@siteCovs)] <- 0
# best2.Ep.Fu2@data@obsCovs[is.na(best2.Ep.Fu2@data@obsCovs)] <- 0
# best2.Ep.Fu2@data@y[is.na(best2.Ep.Fu2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Ep.Fu2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##LANO

```{r, cache=TRUE, echo=FALSE}
# best2.La.No2@data@siteCovs[is.na(best2.La.No2@data@siteCovs)] <- 0
# best2.La.No2@data@obsCovs[is.na(best2.La.No2@data@obsCovs)] <- 0
# best2.La.No2@data@y[is.na(best2.La.No2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.La.No2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##TABR

```{r, cache=TRUE, echo=FALSE}
# best2.Ta.Br2@data@siteCovs[is.na(best2.Ta.Br2@data@siteCovs)] <- 0
# best2.Ta.Br2@data@obsCovs[is.na(best2.Ta.Br2@data@obsCovs)] <- 0
# best2.Ta.Br2@data@y[is.na(best2.Ta.Br2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Ta.Br2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##LACI

```{r, cache=TRUE, echo=FALSE}
# best2.La.Ci2@data@siteCovs[is.na(best2.La.Ci2@data@siteCovs)] <- 0
# best2.La.Ci2@data@obsCovs[is.na(best2.La.Ci2@data@obsCovs)] <- 0
# best2.La.Ci2@data@y[is.na(best2.La.Ci2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.La.Ci2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##EUMA

```{r, cache=TRUE, echo=FALSE}
# best2.Eu.Ma2@data@siteCovs[is.na(best2.Eu.Ma2@data@siteCovs)] <- 0
# best2.Eu.Ma2@data@obsCovs[is.na(best2.Eu.Ma2@data@obsCovs)] <- 0
# best2.Eu.Ma2@data@y[is.na(best2.Eu.Ma2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Eu.Ma2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

##EUPE

```{r, cache=TRUE, echo=FALSE}
# best2.Eu.Pe2@data@siteCovs[is.na(best2.Eu.Pe2@data@siteCovs)] <- 0
# best2.Eu.Pe2@data@obsCovs[is.na(best2.Eu.Pe2@data@obsCovs)] <- 0
# best2.Eu.Pe2@data@y[is.na(best2.Eu.Pe2@data@y)] <- 0
# 
# obs.boot <- mb.gof.test(best2.Eu.Pe2, nsim = 5000)
# ##note that more bootstrap samples are recommended
# ##(e.g., 1000, 5000, or 10 000
# obs.boot
# print(obs.boot, digits.vals = 4, digits.chisq = 4)

```

```{r, echo=FALSE}
# saveRDS(best2.My.Lu2, "best2.My.Lu2.rds")
# saveRDS(best2.My.Th2, "best2.My.Th2.rds")
# saveRDS(preprocov, "preprocov.rds")
# saveRDS(best2.Ta.Br2, "best2.Ta.Br2.rds")
# 
# saveRDS(best2.Pa.He2, "best2.Pa.He2.rds")
# 
# saveRDS(best2.My.Yu2, "best2.My.Yu2.rds")
# 
# saveRDS(best2.My.Lu2, "best2.My.Lu2.rds")
# 
# saveRDS(best2.My.Ev2, "best2.My.Ev2.rds")
# 
# saveRDS(best2.My.Ca2, "best2.My.Ca2.rds")
# 
# saveRDS(best2.My.Ci2, "best2.My.Ci2.rds")
# 
# saveRDS(best2.La.No2, "best2.La.No2.rds")
# 
# saveRDS(best2.La.Ci2, "best2.La.Ci2.rds")
# 
# saveRDS(best2.La.Bl2, "best2.La.Bl2.rds")
# 
# saveRDS(best2.Eu.Ma2, "best2.Eu.Ma2.rds")
# 
# saveRDS(best2.Eu.Pe2, "best2.Eu.Pe2.rds")
# 
# saveRDS(best2.Ep.Fu2, "best2.Ep.Fu2.rds")
# 
# saveRDS(best2.An.Pa2, "best2.An.Pa2.rds")
# 
# saveRDS(FireBats,"firebats.rds")
# 
# saveRDS(summarised_df1, "summarised_df1.rds")


```
