---
title: "Vegetation models"
author: "Derek Corcoran"
date: "August 29, 2016"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE)
```

#Abstract

This webpage will show the results of a bat survey study done in the Plumas National Forest in North California. The objective of this study is to determine the distribution of the different species of bats within the park. In order to do that we have performed occupancy models for the species present in the park. The results of this models will be shown as maps showing the probability of occurence of bats in each point, that is, if you see a value of 1, there is a 100% chance of finding a bat in that point, if there is a value of 0 there is 0% chance of finding that specie in that point, if there is a value of 0.5 there is a 50% chance of finding that specie in that point.

Another result

```{r, message=FALSE, warning=FALSE, echo=FALSE,results='hide'}
#first load libraries
library(raster)
library(rasterVis)
library(maps)
library(maptools)
library(rgdal)
library(latticeExtra)
library(dplyr)
library(knitr)
library(unmarked)
library(lubridate)
library(jpeg)
library(stargazer)
library(xtable)
library(MuMIn)
library(ggplot2)
library(RCurl)
library(foreign)
library(caret)
library(AICcmodavg)
```


```{r,echo=FALSE, warning=FALSE,message=FALSE}
Grandtotal <- read.csv("~/LastBat/Grandtotal.csv")
Grandtotal <- Grandtotal[,-1]

sampling.cov<- Grandtotal[,53:83]
sampling.cov <- sampling.cov[,-c(7,8,17:22)]
#This next step changes according to the models
preprocov <-preProcess(sampling.cov[,c(1:4,7:14)], method = c("center","scale"))
sampling.cov<-predict(preprocov, sampling.cov[,c(1:4,7:14)])

Dailycov <- Grandtotal[,84:110]


preproDaily <-preProcess(Dailycov, method = c("center","scale"))
Dailycov<-predict(preproDaily, Dailycov)

Julian<-Dailycov[,1:3]
Max.hum<-Dailycov[,4:6]
Max.temp<-Dailycov[,7:9]
Mean.hum<-Dailycov[,10:12]
Mean.temp<-Dailycov[,13:15]
Min.hum<-Dailycov[,16:18]
Min.temp<-Dailycov[,19:21]
Sd.hum<-Dailycov[,22:24]
Sd.temp<-Dailycov[,25:27]

Dailycov<- list(Julian,Max.hum, Max.temp, Mean.hum,Mean.temp, Min.hum, Min.temp, Sd.hum, Sd.temp)
names(Dailycov) <- c("Julian", "Maxhum","Maxtemp","Meanhum", "Meantemp","Minhum","Mintemp","sdhum","sdtemp")

```

#Results of species prescence

In this area 0 means absence, and 1 means prescence. This table has for each site (ID), every specie and day, so for example if Mylu1=0, that means that for *Myotis lucifugus* (common name Little Brown bat, was detected on day one for that particular site).

##Here is a key for bat species

- *Myotis yumanensis* (Myyu)
- *Myotis californicus* (Myca)
- *Myotis ciliolabrum* (Myci)
- *Myotis volans* (Myvo)
- *Myotis lucifugus* (Mylu)
- *Parastrellus hesperus* (Pahe)
- *Lasiurus blossevillii* (Labo)
- *Myotis evotis* (Myev)
- *Antrozous pallidus*  **(Anpa)**
- *Eptesicus fuscus* (Epfu)
- *Lasionycteris noctivagans* (Lano)
- *Myotis thysanodes* **(Myth)**
- *Tadarida brasiliensis* (Tabr)
- *Lasiurus cinereus* (Laci)
- *Corynorhinus townsendii* **(Coto)**
- *Euderma maculatum* (Euma)
- *Eumops perotis* (Eupe)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccu <- Grandtotal[,2:52]
```

#Maps predicting the distribution of bats

##Yuma myotis (*Myotis yumanensis*)

```{r, echo=FALSE,message=FALSE}
library(unmarked)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}
#N=49a
BatOccuMyYu<-BatOccu[,1:3]

SimOccuMyYu2<-unmarkedFrameOccu(y = BatOccuMyYu, siteCovs =sampling.cov, obsCovs=Dailycov)


model.Occu1.My.Yu2 <- occu(~ Meantemp + Minhum + Meanhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER ,SimOccuMyYu2)

select.My.Yu2 <- dredge(model.Occu1.My.Yu2, rank = "AICc", subset= `p(Meantemp)`& `p(Meanhum)`& `p(Minhum)`)

best2.My.Yu2<-get.models(select.My.Yu2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
library(texreg)
htmlreg(extract(subset(select.My.Yu2, delta <= 2, recalc.weights = TRUE)), file = "myyu.doc")

htmlreg(extract(subset(select.My.Yu2, delta <= 2, recalc.weights = TRUE)))
```

##California bat (*Myotis californicus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyCa<-BatOccu[,4:6]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}

SimOccuMyCa2<-unmarkedFrameOccu(y = BatOccuMyCa, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ca2 <- occu(~ Maxhum + Meanhum + Meantemp + Mintemp ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyCa2)

select.My.Ca2 <- dredge(model.Occu1.My.Ca2, rank = "AICc", subset= `p(Maxhum)` & `p(Meanhum)` & `p(Meantemp)` & `p(Mintemp)`)

best2.My.Ca2<-get.models(select.My.Ca2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

library(texreg)
htmlreg(extract(subset(select.My.Ca2, delta <= 2, recalc.weights = TRUE)))
```


##Western Small Footed Myotis (*Myotis ciliolabrum*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyCi<-BatOccu[,7:9]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuMyCi2<-unmarkedFrameOccu(y = BatOccuMyCi, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ci2 <- occu(~ Maxhum + Meanhum + sdhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyCi2)

select.My.Ci2 <- dredge(model.Occu1.My.Ci2, rank = "AICc", subset= `p(Maxhum)`  & `p(Meanhum)` & `p(sdhum)`)

best2.My.Ci2<-get.models(select.My.Ci2, 1)[[1]]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
library(texreg)
htmlreg(extract(subset(select.My.Ci2, delta <= 2, recalc.weights = TRUE)))
```

##Hairy-winged bat (*Myotis volans*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuMyVo<-BatOccu[,10:12]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyVo2<-unmarkedFrameOccu(y = BatOccuMyVo, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Vo2 <- occu(~ Maxhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyVo2)

select.My.Vo2 <- dredge(model.Occu1.My.Vo2, rank = "AICc", subset=  `p(Maxhum)`)

best2.My.Vo2<-get.models(select.My.Vo2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
library(texreg)
htmlreg(extract(subset(select.My.Vo2, delta <= 2, recalc.weights = TRUE)))

```

##Little Brown bat (*Myotis lucifugus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyLu<-BatOccu[,13:15]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyLu2<-unmarkedFrameOccu(y = BatOccuMyLu, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Lu2 <- occu(~ sdtemp ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyLu2)

select.My.Lu2 <- dredge(model.Occu1.My.Lu2, rank = "AICc", subset= `p(sdtemp)`)

best2.My.Lu2<-get.models(select.My.Lu2, 1)[[1]]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}
library(texreg)

htmlreg(extract(subset(select.My.Lu2, delta <= 2, recalc.weights = TRUE)))
```


##Western Red Bat (*Lasiurus blossevillii*)


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}

BatOccuLaBl<-BatOccu[,19:21]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}

SimOccuLaBl2<-unmarkedFrameOccu(y = BatOccuLaBl, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.La.Bl2 <- occu(~ sdtemp ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuLaBl2)

select.La.Bl2 <- dredge(model.Occu1.La.Bl2, rank = "AICc", subset = `p(sdtemp)`)

best2.La.Bl2<-get.models(select.La.Bl2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

library(texreg)
htmlreg(extract(subset(select.La.Bl2, delta <= 2, recalc.weights = TRUE)))
```

##Long-eared Bat (*Myotis evotis*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuMyEv<-BatOccu[,22:24]
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyEv2<-unmarkedFrameOccu(y = BatOccuMyEv, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Ev2 <- occu(~ Maxhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyEv2)

select.My.Ev2 <- dredge(model.Occu1.My.Ev2, rank = "AICc", subset= `p(Maxhum)`)

best2.My.Ev2<-get.models(select.My.Ev2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.My.Ev2, delta <= 2, recalc.weights = TRUE)))
```

## Pallid Bat (*Antrozous pallidus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuAnPa<-BatOccu[,25:27]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49

SimOccuAnPa2<-unmarkedFrameOccu(y = BatOccuAnPa, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.An.Pa2 <- occu(~ Julian ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuAnPa2)

select.An.Pa2 <- dredge(model.Occu1.An.Pa2, rank = "AICc", subset= `p(Julian)`)

best2.An.Pa2<-get.models(select.An.Pa2, 1)[[1]]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.An.Pa2, delta <= 2, recalc.weights = TRUE)))
```


###Fringed Bat (*Myotis thysanoides*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuMyTh<-BatOccu[,34:36]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuMyTh2<-unmarkedFrameOccu(y = BatOccuMyTh, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.My.Th2 <- occu(~ Meanhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuMyTh2)


select.My.Th2 <- dredge(model.Occu1.My.Th2, rank = "AICc", subset= `p(Meanhum)`)

best2.My.Th2<-get.models(select.My.Th2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.My.Th2, delta <= 2, recalc.weights = TRUE)))
```

##Townsend’s Long-eared Bat (*Corynorhinus townsendii*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuCoTo<-BatOccu[,43:45]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuCoTo2<-unmarkedFrameOccu(y = BatOccuCoTo, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Co.To2 <- occu(~ Meanhum + Mintemp + sdhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuCoTo2)


select.Co.To2 <- dredge(model.Occu1.Co.To2, rank = "AICc", subset= `p(Meanhum)`&`p(Mintemp)` &`p(sdhum)`)


best2.Co.To2<-get.models(select.Co.To2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

htmlreg(extract(subset(select.Co.To2, delta <= 2, recalc.weights = TRUE)))
```

##The western pipistrelle (*Parastrellus hesperus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
BatOccuPaHe<-BatOccu[,16:18]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
SimOccuPaHe2<-unmarkedFrameOccu(y = BatOccuPaHe, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Pa.He2 <- occu(~ Julian + Maxhum + Mintemp ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuPaHe2)

select.Pa.He2 <- dredge(model.Occu1.Pa.He2,rank = "AICc", subset= `p(Julian)` & `p(Maxhum)` & `p(Mintemp)`)


best2.Pa.He2<-get.models(select.Pa.He2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.Pa.He2, delta <= 2, recalc.weights = TRUE)))
```

##big brown bat (*Eptesicus fuscus*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuEpFu<-BatOccu[,28:30]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuEpFu2<-unmarkedFrameOccu(y = BatOccuEpFu, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Ep.Fu2 <- occu(~ Julian + Meantemp + Meanhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuEpFu2)


select.Ep.Fu2 <- dredge(model.Occu1.Ep.Fu2, rank = "AICc", subset=  `p(Julian)` & `p(Meantemp)` & `p(Meanhum)`)

best2.Ep.Fu2<-get.models(select.Ep.Fu2, 1)[[1]]

```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.Ep.Fu2, delta <= 2, recalc.weights = TRUE)))
```

##silver-haired bat (*Lasionycteris noctivagans*)

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
BatOccuLaNo<-BatOccu[,31:33]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuLaNo2<-unmarkedFrameOccu(y = BatOccuLaNo, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.La.No2 <- occu(~ Meantemp + Maxhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuLaNo2)

select.La.No2 <- dredge(model.Occu1.La.No2, rank = "AICc", subset= `p(Meantemp)` & `p(Maxhum)`)

best2.La.No2<-get.models(select.La.No2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.La.No2, delta <= 2, recalc.weights = TRUE)))
```


##Brazilian free-tailed bat (*Tadarida brasiliensis*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccuTaBr<-BatOccu[,37:39]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuTaBr2<-unmarkedFrameOccu(y = BatOccuTaBr, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Ta.Br2 <-occu(~ Meanhum + sdhum + Minhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER,  SimOccuTaBr2)

select.Ta.Br2 <- dredge(model.Occu1.Ta.Br2,rank = "AICc", subset= `p(sdhum)` & `p(Meanhum)`& `p(Minhum)`)


best2.Ta.Br2<-get.models(select.Ta.Br2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.Ta.Br2, delta <= 2, recalc.weights = TRUE)))
```


##hoary bat (*Lasiurus cinereus*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccuLaCi<-BatOccu[,40:42]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuLaCi2<-unmarkedFrameOccu(y = BatOccuLaCi, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.La.Ci2 <- occu(~  Julian + Meantemp + sdtemp + Minhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuLaCi2)


select.La.Ci2 <- dredge(model.Occu1.La.Ci2, rank = "AICc", subset= `p(Julian)` & `p(Meantemp)`& `p(sdtemp)`& `p(Minhum)`)


best2.La.Ci2<-get.models(select.La.Ci2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.La.Ci2, delta <= 2, recalc.weights = TRUE)))
```

##Spotted bat (*Euderma maculatum*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccuEuMa<-BatOccu[,46:48]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results='hide'}
#N=49
SimOccuEuMa2<-unmarkedFrameOccu(y = BatOccuEuMa, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Eu.Ma2 <- occu(~ Meantemp + Maxtemp + Maxhum ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuEuMa2)

select.Eu.Ma2 <- dredge(model.Occu1.Eu.Ma2, rank = "AICc", subset= `p(Meantemp)`& `p(Maxtemp)` & `p(Maxhum)`)

best2.Eu.Ma2<-get.models(select.Eu.Ma2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

library(texreg)
htmlreg(extract(subset(select.Eu.Ma2, delta <= 2, recalc.weights = TRUE)))
```


## western mastiff bat (*Eumops perotis*)

```{r,echo=FALSE, warning=FALSE,message=FALSE}
BatOccuEuPe<-BatOccu[,49:51]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results="hide"}
#N=49

SimOccuEuPe2<-unmarkedFrameOccu(y = BatOccuEuPe, siteCovs =sampling.cov, obsCovs=Dailycov)

model.Occu1.Eu.Pe2 <- occu(~ Maxhum + Meanhum + Minhum + sdhum  ~ AreaPerHa + Average + Sd + count + CANOPY.COVER + WOODY + HERBACIOUS + GRASS + NAKED.SOIL + ROCKY + DOWN.WOOD + LEAF.LITTER, SimOccuEuPe2)


select.Eu.Pe2 <- dredge(model.Occu1.Eu.Pe2, rank = "AICc", subset= `p(Minhum)`& `p(sdhum)` & `p(Meanhum)`& `p(Maxhum)`)

best2.Eu.Pe2<-get.models(select.Eu.Pe2, 1)[[1]]
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results="asis"}

library(texreg)
htmlreg(extract(subset(select.Eu.Pe2, delta <= 2, recalc.weights = TRUE)))
```

```{r, echo=FALSE}

panel.hist <- function(x, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(usr[1:2], 0, 1.5) )
    h <- hist(x, plot = FALSE)
    breaks <- h$breaks; nB <- length(breaks)
    y <- h$counts; y <- y/max(y)
    rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}

panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- cor(x, y)
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(0.5, 0.5, txt, cex = cex.cor * r)
}

pairs(sampling.cov, lower.panel = panel.smooth, upper.panel = panel.cor, diag.panel = panel.hist)
```


```{r, echo=FALSE}
sampling.cov <- readRDS("sampling.cov.rds")

#generate a dataframe filed with means called output
means <- colMeans(sampling.cov, na.rm = TRUE)
output <- matrix(ncol=ncol(sampling.cov), nrow=65)

for(i in 1:ncol(sampling.cov)){
  output[,i] <-  rep(means[i], times = 65)
  
}
output <- data.frame(output)
colnames(output) <- colnames(sampling.cov)

##generate max min matrix

maxmin <- matrix(ncol=ncol(sampling.cov), nrow=2)
rownames(maxmin) <- c("max", "min")
colnames(maxmin) <- colnames(sampling.cov)

for(i in 1:ncol(sampling.cov)){
  maxmin[1,i] <-  max(sampling.cov[,i], na.rm = TRUE)
  maxmin[2,i] <-  min(sampling.cov[,i], na.rm = TRUE)
}

```

#Cannopy cover
```{r, cache=TRUE, echo=FALSE}

output$CANOPY.COVER <-seq(from = min(sampling.cov$CANOPY.COVER, na.rm = TRUE), to = max(sampling.cov$CANOPY.COVER, na.rm = TRUE), length.out = 65)

#Tabr

CanopyPredicted <- predict(best2.Ta.Br2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

tabrcanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "TABR") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

tabrcanopyresp

```

```{r, cache=TRUE, echo=FALSE}

#Myyu

CanopyPredicted <- predict(best2.My.Yu2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

myyucanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYYU") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")


#Mylu

CanopyPredicted <- predict(best2.My.Lu2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

mylucanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYLU") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Myci

CanopyPredicted <- predict(best2.My.Ci2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

mycicanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYCI") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Lano

CanopyPredicted <- predict(best2.La.No2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

lanocanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "LANO") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Eupe

CanopyPredicted <- predict(best2.Eu.Pe2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

eupecanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "EUPE") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")


#Epfu

CanopyPredicted <- predict(best2.Ep.Fu2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

epfucanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "EPFU") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Anpa

CanopyPredicted <- predict(best2.An.Pa2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

anpacanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "ANPA") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Myev

CanopyPredicted <- predict(best2.My.Ev2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

myevcanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYEV") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

#Myth

CanopyPredicted <- predict(best2.My.Th2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, CanopyPredicted)

mythcanopyresp <- ggplot(OutputInt, aes(x = CANOPY.COVER, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYTH") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Canopy cover") + ylab("Occupancy")

library(gridExtra)

grid.arrange(epfucanopyresp, myevcanopyresp, mylucanopyresp, lanocanopyresp, myyucanopyresp,anpacanopyresp,eupecanopyresp, mycicanopyresp,  mythcanopyresp, ncol = 3)


```


#Basal Area

```{r, echo=FALSE}
sampling.cov <- readRDS("sampling.cov.rds")

#generate a dataframe filed with means called output
means <- colMeans(sampling.cov, na.rm = TRUE)
output <- matrix(ncol=ncol(sampling.cov), nrow=65)

for(i in 1:ncol(sampling.cov)){
  output[,i] <-  rep(means[i], times = 65)
  
}
output <- data.frame(output)
colnames(output) <- colnames(sampling.cov)

##generate max min matrix

maxmin <- matrix(ncol=ncol(sampling.cov), nrow=2)
rownames(maxmin) <- c("max", "min")
colnames(maxmin) <- colnames(sampling.cov)

for(i in 1:ncol(sampling.cov)){
  maxmin[1,i] <-  max(sampling.cov[,i], na.rm = TRUE)
  maxmin[2,i] <-  min(sampling.cov[,i], na.rm = TRUE)
}

```

```{r, cache=TRUE, echo=FALSE}

output$AreaPerHa <-seq(from = min(sampling.cov$AreaPerHa, na.rm = TRUE), to = max(sampling.cov$AreaPerHa, na.rm = TRUE), length.out = 65)

#Myci

BasalPredicted <- predict(best2.My.Ci2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

mycibasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYCI") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")

mycibasalresp

```


```{r, cache=TRUE, echo=FALSE}

#Labl

BasalPredicted <- predict(best2.La.Bl2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

lablbasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "LABL") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")


#Myev

BasalPredicted <- predict(best2.My.Ev2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

myevbasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYEV") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")

#Myth

BasalPredicted <- predict(best2.My.Th2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

mythbasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "MYTH") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")

#Pahe

BasalPredicted <- predict(best2.Pa.He2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

pahebasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "PAHE") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")

#Laci

BasalPredicted <- predict(best2.La.Ci2, type = "state", predict(preprocov, output))
OutputInt <- cbind(output, BasalPredicted)

lacibasalresp <- ggplot(OutputInt, aes(x = AreaPerHa, y = Predicted))  + geom_ribbon(aes(ymax = upper, ymin = lower), alpha = 0.5) + geom_line(size = 1)+ ylim(c(0,1))+ labs(title = "LACI") + theme(
  panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  plot.background = element_rect(fill = "transparent",colour = NA)
)+
  theme(axis.line.x = element_line(color="black", size = 0.5),
        axis.line.y = element_line(color="black", size = 0.5))+ xlab("Basal Area") + ylab("Occupancy")


library(gridExtra)

grid.arrange(myevbasalresp, lacibasalresp, lablbasalresp, mycibasalresp, mythbasalresp, pahebasalresp,  ncol = 3)


```